# Reproducible Research: Peer Assessment 1

Reproducible Research: Peer Assessment 1
========================================================
```{r}
setwd("Coursera/repdata/")
```
## Down dload data one time

#download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip","repdata-data-activity.zip","curl")

#unzip data
#unzip("repdata-data-activity.zip")

## Loading and preprocessing the data
1. Load the data (i.e. read.csv())

2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
pa1 <-read.csv("./activity.csv",sep=",",head=T,colClasses=c("integer","Date","integer"))
head(pa1)
```

## What is mean total number of steps taken per day?

* calculate steps after Splitting data by date. ignore NAs
* Plot histogamme.
* Calculate mean & medaine.

```{r}
perDayPA1 <- sapply(split(pa1$steps,pa1$date),sum,na.rm=T)

hist(perDayPA1)

pa1mean<-mean(perDayPA1 )
pa1median<-median(perDayPA1)
```
Mean of per day steps : **`r pa1mean`** 
Mediane of daily steps per day : **`r pa1median`.** 

## What is the average daily activity pattern?
```{r}
avgDailyAct<-sapply(split(pa1$steps,pa1$interval),mean,na.rm=T)
int<- unique(pa1$interval)
plot(x=int,y=avgDailyAct,type='l',xlab='Interval - 5-minute',ylab='Average steps')

intTot<-sapply(split(pa1$steps,pa1$interval),sum,na.rm=T)
i <- which.max(intTot)
intMax <- int[i]

```
## Imputing missing values

```{r}
nrow(na.omit(pa1))
cleanpa1<-pa1
for(i in 1:nrow(pa1)){
    if(is.na(pa1$steps[i])){
        cleanpa1$steps[i]<- avgDailyAct[(i %% 288)+1]
    }
}
```
newPerDayPA1 <- sapply(split(cleanpa1$steps,cleanpa1$date),sum,na.rm=T)
hist(newPerDayPA1)

newPa1mean <- mean(newPerDayPA1)
newPa1median <- median(newPerDayPA1)

Mean of per day steps : **`r newPa1mean`** 
Mediane of daily steps per day : **`r newPa1median`.** 

## Are there differences in activity patterns between weekdays and weekends?

```{r}
#install.packages("reshape")
library("reshape")
Sys.setlocale("LC_TIME", "English")
isWeekEnd<-function(day){
    if(weekdays(day)  %in% c( "Saturday","Sunday")){
        "yes"
    }
    else{
        "no"
    }      
}
```


```{r}
isweekend <- sapply(pa1$date,isWeekEnd)
pa1 <- cbind(pa1,isweekend)
pa1splits <- split(pa1,pa1$isweekend)
weekdaypa1<-pa1splits$no
weekendpa1<-pa1splits$yes
avgPerDayIntWeekDays<-sapply(split(weekdaypa1$steps,weekdaypa1$interval),sum,na.rm=T)
avgPerDayIntWeekEnds<-sapply(split(weekendpa1$steps,weekendpa1$interval),sum,na.rm=T)
int<- unique(pa1$interval)
weekdaypa12 <- data.frame(steps=avgPerDayIntWeekDays,interval=int,nature="no")
weekendpa12 <- data.frame(steps=avgPerDayIntWeekEnds,interval=int,nature="yes")
CombinedData <- rbind(weekdaypa12,weekendpa12)
```

    
```{r fig.width=15}
library("lattice")
xyplot(data=CombinedData ,steps~interval|nature,layout=c(1,2),type="l",ylab="Number of steps",lwd=2)
